A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-19 tex/codatadp.tex
more

%    * when looking at the ground theory:
%        enough to consider acyclicity -- no way to specify infinite objects
%        otherwise

>>>>

When looking at the ground theory, induction can be replaced by the acyclicity
axiom schema, which states that any ground constructor term cannot be equal to
a variable it contains \cite{xxx}. Dually, coinduction can be replaced by the
bisimilarity axiom schema, which asserts that two values having the same
corecursive specification---e.g., $x \teq \const{C}(x)$ and $y \teq
\const{C}(y)$---must be identical.

\begin{report}
PROVE?
\end{report}

%    * :
%        enough to consider acyclicity -- no way to specify infinite objects
%        otherwise
